%=============================================================================
\subsection{Checklist}
\label{getting-on-the-grid---checklist}
%=============================================================================

\subsubsection{Your Grid certificate}\label{your-grid-certificate}

\begin{itemize}
\tightlist
\item
  I have requested a grid certificate from the
  \href{http://ngs.ac.uk/ukca}{UK Certificate Authority} (UKCA).
\item
  I know where my nearest
  \href{https://portal.ca.grid-support.ac.uk/caportal/pub/viewralist}{Registration
  Authority} (RA) is.
\item
  I have visited my nearest RA and confirmed my identity.
\item
  I have downloaded my grid certificate .p12 file and installed it in my
  browser.
\item
  I have backed up my grid certificate .p12 file in a secure location.
\end{itemize}

%-----------------------------------------------------------------------------
\subsubsection{Joining a Virtual Organisation -- Checklist}
\label{joining-a-virtual-organisation---checklist}
%-----------------------------------------------------------------------------

\begin{itemize}
\tightlist
\item
  I have submitted a request to join a Virtual Organisation (VO).
\item
  My request has been approved by a VO manager and I have received email
  confirmation of the approval.
\item
  I have followed all of the instructions in the confirmation email.
\end{itemize}

%-----------------------------------------------------------------------------
\subsubsection{First steps with GridPP DIRAC}
\label{first-steps-with-gridpp-dirac}
%-----------------------------------------------------------------------------

\begin{itemize}
\tightlist
\item
  I have accessed the \href{https://dirac.gridpp.ac.uk}{GridPP DIRAC web
  portal} with my Grid certificate-enabled browser.
\item
  I am recognised by the \href{https://dirac.gridpp.ac.uk}{GridPP DIRAC
  web portal} as a \emph{Visitor}.
\item
  I have joined the
  \href{https://mailman.ic.ac.uk/mailman/listinfo/gridpp-dirac-users}{GridPP
  DIRAC mailing list}.
\end{itemize}
