%=============================================================================
\subsection{Joining a Virtual Organisation}
\label{sec:joinvo}
%=============================================================================
Your Grid certificate identifies you to the grid as an individual user,
but it's not enough on its own to allow you to use grid resources; you
also need to join a \term{Virtual Organisation} (VO). These are essentially
just user groups - typically one per experiment - and individual
Resource Centres (RCs) can choose to support work by users of a
particular VO. Most RCs support the four VOs associated with the Large
Hadron Collider (LHC) experiments. The sign-up procedure varies from VO
to VO. UK-based VOs typically require a manual approval step, while LHC
VOs require an active CERN account. If you are already part of an
experiment that is represented by a VO, they should provide you with any
specific instructions you need to join.

If you're interesting in using the grid but are not (yet) working as
part of a user community already represented by a VO, worry not. GridPP
have created a catch-all VO -
\href{https://voms.gridpp.ac.uk:8443/voms/gridpp/}{\texttt{gridpp}} -
and four Regional Virtual Organisations (RVOs) corresponding to the four
Tier 2s that can be joined to test out what the grid has to offer. Once
you have used these ``incubator'' VOs to see if the Grid meets your
needs, you can then think about creating your own Virtual Organisation
to represent your user community.

\begin{infobox}{Is there a VO for you already?}
\emph{Your user community may already have a VO associated with it. Check the
GridPP wiki page of supported VOs to see if you can join that to speed
things up.}
\end{infobox}

%-----------------------------------------------------------------------------
\subsubsection{Joining an incubator VO}
\label{joining-an-incubator-vo}
%-----------------------------------------------------------------------------
\begin{infobox}{Just browsing}
\emph{Some users have reported that the VOMS registration described below
fails using the Safari web browser. We have tried and tested the process
using Mozilla Firefox.}
\end{infobox}

\begin{infobox}{Trusting the VOMS servers}
\emph{Please ignore any ``untrusted connection'' warnings when accessing the
VOMS server pages. GridPP is aware that the VOMS server uses unsigned
certificates, but this situation is unlikely to be resolved any time
soon.}
\end{infobox}

%-----------------------------------------------------------------------------
\subsubsection{Joining the GridPP VO}
\label{joining-the-gridpp-vo}
%-----------------------------------------------------------------------------

To join the
\href{https://voms.gridpp.ac.uk:8443/voms/gridpp}{\texttt{gridpp}} VO,
visit
\href{https://voms.gridpp.ac.uk:8443/voms/gridpp/register/start.action}{this
page} using a browser that has your grid certificate installed and
follow the instructions.

%-----------------------------------------------------------------------------
\subsubsection{Joining a Regional VO}
\label{joining-a-regional-vo}
%-----------------------------------------------------------------------------
Likewise, you can join one of the four regional VOs:

\begin{itemize}
\item
\texttt{vo.londongrid.ac.uk}
\item
\texttt{vo.northgrid.ac.uk}
\item
\texttt{vo.scotgrid.ac.uk}
\item
\texttt{vo.southgrid.ac.uk}
\end{itemize}

\begin{infobox}{Confirming VO your membership}
\emph{Your VO membership request needs to be confirmed manually by one of the
VO administrators, so please wait for the membership confirmation email
to arrive before proceeding. You may wish to keep an eye on your junk
folder(s) too.}
\end{infobox}

Once you have joined a VO, congratulations - you are ready to start
using the Grid!
