%=============================================================================
\subsection{Testing}
\label{getting-on-the-grid---testing}
%=============================================================================

\subsubsection{Your Grid certificate}
\label{your-grid-certificate-testing}

\begin{itemize}
\tightlist
\item
  \textbf{Viewing your certificate details}: visit
  \href{https://portal.ca.grid-support.ac.uk/caportal/cert_owner}{this
  website} with the broswer in which your certificate is installed. You
  should see your grid certificate details displayed.
\end{itemize}

\subsubsection{Joining a Virtual Organisation}
\label{joining-a-virtual-organisation-testing}

\begin{itemize}
\tightlist
\item
  \textbf{Joining the GridPP VO}: Click
  \href{https://voms.gridpp.ac.uk:8443/voms/gridpp/user/search.action}{here}.
  If your request has been approved and confirmed, you should be listed
  as a VO member.
\item
  \textbf{Joining a Regional VO}: Click on
  \href{https://voms.gridpp.ac.uk:8443/voms/vo.londongrid.ac.uk/user/search.action}{\texttt{vo.londongrid.ac.uk}},
  \href{https://voms.gridpp.ac.uk:8443/voms/vo.northgrid.ac.uk/user/search.action}{\texttt{vo.northgrid.ac.uk}},
  \href{https://voms.gridpp.ac.uk:8443/voms/vo.scotgrid.ac.uk/user/search.action}{\texttt{vo.scotgrid.ac.uk}},
  or
  \href{https://voms.gridpp.ac.uk:8443/voms/vo.southgrid.ac.uk/user/search.action}{\texttt{vo.southgrid.ac.uk}}
  (depending on which VO you have attempted to join). If your request
  has been approved and confirmed, you should be listed as a VO member.
\end{itemize}

\subsubsection{First steps with DIRAC}
\label{first-steps-with-dirac-testing}

\begin{itemize}
\tightlist
\item
  \textbf{Accessing the GridPP DIRAC server}: access
  https://dirac.gridpp.ac.uk with your browser. If your grid certificate
  has been successfully installed in your browser, you should be asked
  to identify yourself with the certificate in question. You will then
  see the GridPP DIRAC server homepage. Check the bottom right-hand
  corner - if you can only see \emph{Visitor} and \textbf{not} your
  username and DN, something has gone wrong and you are not (or rather,
  your certificate is not) not registered with the GridPP DIRAC server.
\item
  \textbf{Joining the GridPP DIRAC mailing list}: once you have
  \emph{subscribed} and have \emph{been approved}, you should be able to
  view the
  \href{https://mailman.ic.ac.uk/mailman/roster/gridpp-dirac-users}{subscribers
  list} from the
  \href{https://mailman.ic.ac.uk/mailman/listinfo/gridpp-dirac-users}{list
  homepage} and confirm that you are indeed on it.
\end{itemize}
