%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Putting Data on the Grid}
\label{sec:griddata}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We've now moved the local example workflow to the Grid.
However,
we've still only used data that's been present on our local system, and
we've manually retrieved the output to our local system. To harness the
full power of the Grid, we'll need to put data on it. We'll use tools
provided with DIRAC to do this, namely:

\begin{itemize}
\tightlist
\item The DIRAC File Catalog Command Line Interface (DFC CLI);
\item The DIRAC command line tools;
\item Some first steps with the DFC's metadata functionality.
\end{itemize}

First, though, let's look at some basic concepts in grid-based data
management.

%=============================================================================
\subsection{Storage Elements, File Catalogs, and Replicas}
\label{storage-elements-file-catalogs-and-replicas}
%=============================================================================
The first thing to wrap one's head around with distributed computing is
the notion that you don't really need to care about where your data is
stored. You may well be used to this concept if you've dealt with
cloud-based storage services such as Dropbox, Google Drive, or even
Amazon S3 storage. Your files are on one or more servers
\emph{somewhere}, and all that you need to know are the file names and
the directories that they're in to access them later.

It's the same with the grid. You upload your files to a grid
\textbf{Storage Element} (SE) and label them with a \textbf{Logical File
Name} (LFN) that gets registered in something called a \textbf{File
Catalog}. If you make copies of a particular file - a \textbf{replica} -
on one or more additional SEs, the locations of these replicas are
recorded in the File Catalog too.

\begin{infobox}{Storage Elements and replicas}
\emph{With most cloud-based storage services, you won't even really care about
the Storage Elements (or their non-grid equivalents, whatever the they
happen to be called) and file replicas. However, when considering
running grid jobs at a particular grid site, the location of your
replicas can matter (you'll want to make sure your data is available at
sites that will run jobs for your Virtual Organisation). We'll come back
to all of these concepts - and provide concrete examples - later.}
\end{infobox}

The GridPP DIRAC system provides a suite of tools to help you manage all
of this. If you're familiar with UNIX-based file systems you should find
it all pretty straightforward. We'll start with the
DIRAC File Catalog Command Line Interface.

\input{griddata/dfccli}

\input{griddata/cltools}

\input{griddata/metadata}

\input{griddata/checklist}

\input{griddata/testing}

