%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Troubleshooting}
\label{sec:troubleshooting}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This section contains brief notes on specific problems users have
encountered when working on specific systems, generally raised via the
\href{http://github.com/gridpp/user-guides/issues}{GitHub Issues page}.

\subsection{Ganga}\label{ganga}

\emph{Ganga isn't working.}

If you're having problems with Ganga, the best thing to do is to
\href{https://github.com/ganga-devs/ganga/issues}{raise an issue} with
the Ganga dev team through the
\href{https://github.com/ganga-devs/ganga/}{GitHub repository}. At the
time of writing, we've been using Ganga version 6.3.1 - but as Ganga is
under active development this may change so you may want to
\href{https://github.com/ganga-devs/ganga}{watch the repository too}.

\emph{Ganga throws errors relating to not being able lock files.}

If the file system your cluster is based on can't handle (or hasn't been
set up to allow) file locks, which Ganga uses. If your home directory is
on such a file system (e.g.~NFS), files in your
\texttt{\textasciitilde{}/gangadir} won't be lockable and Ganga won't
work. Assuming your cluster can't be reconfigured, the simplest thing to
do is change the location of your \texttt{gangadir} to somewhere that
can handle file locks, such as a scratch directory on the cluster. To do
this, set the \texttt{gangadir} option in
\texttt{\textasciitilde{}/.gangarc} to something like:

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{gangadir} \NormalTok{= /scratch/alovelace/gangadir}
\end{Highlighting}
\end{Shaded}

and restart Ganga in the usual way.

\subsection{Miscellaneous problems}

\emph{My problem isn't listed here and search engines aren't helping
either.}

Raise an issue on the
\href{http://github.com/gridpp/user-guides/issues}{GitHub issues page}
and we'll see if we can help!

Good luck!
